Problem Set 1

### 2019-09-13 content/assignment/01-problem-set.Rmd
Minor fixes to problem set 1 page (links and formatting)

- [<i class="fas fa-file-pdf"></i> `Download as PDF`](/homeworks/01-problem-set.pdf)
- [<i class="fab fa-markdown"></i> `Download Markdown`](/homeworks/01-r-problem-set.Rmd)

@@

## 13.
Make another plot similar to 12, except this time use GDP per Capita (`gdp`) as `y`. Feel free to try to put a regression line with `geom_smooth()`!^[If you do, be sure to set its data to the full `freedom`, not just your three countries!]^[Those of you in my Development course, you just made my graphs from [Lesson 2](https://devf19.classes.ryansafner.com/slides/02-slides#23)!]

>>>>

- [<i class="fas fa-file-pdf"></i> `Download as PDF`](/homeworks/01-problem-set-pdf.pdf)
- [<i class="fab fa-markdown"></i> `Download Markdown`](/homeworks/01-problem-set.Rmd)

@@

## 13.
Make another plot similar to 12, except this time use GDP per Capita (`gdp`) as `y`. Feel free to try to put a regression line with `geom_smooth()`!^[If you do, be sure to set its data to the full `freedom`, not just your three countries!] Those of you in my Development course, you just made my graphs from [Lesson 2](https://devf19.classes.ryansafner.com/slides/02-slides#23)!
